\section{Environment configuration}
To use the cluster correctly, it is first necessary to configure the 
environment responsible for its instantiation. Specifically, the following
steps are required:
\begin{itemize}
	\item Install \textit{libvirt}, ensuring the user has the necessary permissions,
    along with other required applications.
	\item Create the system image that will be used to boot the virtual
    machines (VMs).
\end{itemize}
To automate this process, we developed a Bash script that configures 
everything needed on Arch Linux-based distributions.

The reason for this restriction is that the image creation process uses 
an Arch Linux-exclusive tool called \textit{Archiso}\cite{4}. 
This tool allows the creation of system images and is typically used 
to generate customized installation Live environments.

Using \textit{Archiso}, we organized the filesystem, configured services, selected 
installed packages, and set up the bootloader.

Our objective was to minimize the image size by removing unnecessary programs 
and/or replacing them with lighter alternatives. We also chose \textit{Syslinux} 
as the bootloader due to its lightweight nature compared to the standard 
\textit{GRUB}, setting a boot timeout of zero to reduce startup times.

By default, the bootloader has an average wait timeout of 5 seconds.
This delay allows users to select an operating system or access the BIOS menu.
However, in our case, this functionality is unnecessary, and the 5-second delay is 
simply wasted time.
To eliminate this delay, we modify the configuration file 
\begin{verbatim}
\texttt{env_setup/iso_creation/syslinux/syslinux.cfg}
\end{verbatim}
by adding the line:
\begin{verbatim}
PROMPT 0
\end{verbatim}
This change ensures that the bootloader skips the UI entirely and immediately loads the default 
operating system (Arch Linux in our case).
While this modification is not strictly required for system functionality, 
its simplicity makes it a worthwhile optimization, reducing boot time from over 5 seconds to 
less than 1 second per node.


Once the image is created, it is copied into the default 	\textit{libvirt} directories
(\texttt{/var/lib/libvirt/images/}) so that \textit{libvirt} can use it during 
the VM creation process.

When the Bash script is executed, it performs the following steps:
\begin{itemize}
	\item Installs the required packages for virtualization.
	\item Grants the current user the necessary permissions to use \textit{libvirt} 
    without requiring root privileges.
  \item Uses \textit{Archiso} to create the system image.
\end{itemize}
      Initially, we considered using a precompiled image, but we opted for this 
      approach because it is significantly more secure and eliminates the need to 
      manually track system versioning. Additionally, it provides a simple update 
      process for the cluster. Specifically, updating the cluster only requires modifying 
      the \textit{Archiso} configuration and re-executing the setup script to apply 
      the desired updates.
